
```{r abstractst, echo=FALSE, warning=FALSE, message=FALSE}

library(readxl)
library(tidyverse)

abstracts <- read_csv("abstracts/dissertations_2021.csv") %>%
  arrange(LastName) %>%
  filter(initial == "T")

TagFalse <- "Other."

i <- 1L
```


## Surnames beginning with T {-}

**Name:** `r abstracts$FirstName[i]` `r abstracts$LastName[i]`

**Supervisor:** `r abstracts$SFirstName[i]` `r abstracts$SLastName[i]`

**Title:** `r abstracts$Title[i]`

**Abstract:** `r abstracts$Abstract[i]`

**Tags:** `r ifelse(abstracts$Theme1[i] == "NA",TagFalse, abstracts$Theme1[i])``r ifelse(abstracts$Theme2[i] == "NA"," ", paste(", ", abstracts$Theme2[i]))``r ifelse(abstracts$Theme3[i] == "NA"," ", paste(", ", abstracts$Theme3[i]))``r ifelse(abstracts$Theme4[i] == "NA"," ", paste(", ", abstracts$Theme4[i]))`

---

```{r, echo = FALSE}
i <- i + 1L
```

**Name:** `r abstracts$FirstName[i]` `r abstracts$LastName[i]`

**Supervisor:** `r abstracts$SFirstName[i]` `r abstracts$SLastName[i]`

**Title:** `r abstracts$Title[i]`

**Abstract:** `r abstracts$Abstract[i]`

**Tags:** `r ifelse(abstracts$Theme1[i] == "NA",TagFalse, abstracts$Theme1[i])``r ifelse(abstracts$Theme2[i] == "NA"," ", paste(", ", abstracts$Theme2[i]))``r ifelse(abstracts$Theme3[i] == "NA"," ", paste(", ", abstracts$Theme3[i]))``r ifelse(abstracts$Theme4[i] == "NA"," ", paste(", ", abstracts$Theme4[i]))`

---


```{r, echo = FALSE}
i <- i + 1L
```

**Name:** `r abstracts$FirstName[i]` `r abstracts$LastName[i]`

**Supervisor:** `r abstracts$SFirstName[i]` `r abstracts$SLastName[i]`

**Title:** `r abstracts$Title[i]`

**Abstract:** `r abstracts$Abstract[i]`

**Tags:** `r ifelse(abstracts$Theme1[i] == "NA",TagFalse, abstracts$Theme1[i])``r ifelse(abstracts$Theme2[i] == "NA"," ", paste(", ", abstracts$Theme2[i]))``r ifelse(abstracts$Theme3[i] == "NA"," ", paste(", ", abstracts$Theme3[i]))``r ifelse(abstracts$Theme4[i] == "NA"," ", paste(", ", abstracts$Theme4[i]))`

---


```{r, echo = FALSE}
i <- i + 1L
```

**Name:** `r abstracts$FirstName[i]` `r abstracts$LastName[i]`

**Supervisor:** `r abstracts$SFirstName[i]` `r abstracts$SLastName[i]`

**Title:** `r abstracts$Title[i]`

**Abstract:** `r abstracts$Abstract[i]`

**Tags:** `r ifelse(abstracts$Theme1[i] == "NA",TagFalse, abstracts$Theme1[i])``r ifelse(abstracts$Theme2[i] == "NA"," ", paste(", ", abstracts$Theme2[i]))``r ifelse(abstracts$Theme3[i] == "NA"," ", paste(", ", abstracts$Theme3[i]))``r ifelse(abstracts$Theme4[i] == "NA"," ", paste(", ", abstracts$Theme4[i]))`

---


```{r, echo = FALSE}
i <- i + 1L
```

**Name:** `r abstracts$FirstName[i]` `r abstracts$LastName[i]`

**Supervisor:** `r abstracts$SFirstName[i]` `r abstracts$SLastName[i]`

**Title:** `r abstracts$Title[i]`

**Abstract:** `r abstracts$Abstract[i]`

**Tags:** `r ifelse(abstracts$Theme1[i] == "NA",TagFalse, abstracts$Theme1[i])``r ifelse(abstracts$Theme2[i] == "NA"," ", paste(", ", abstracts$Theme2[i]))``r ifelse(abstracts$Theme3[i] == "NA"," ", paste(", ", abstracts$Theme3[i]))``r ifelse(abstracts$Theme4[i] == "NA"," ", paste(", ", abstracts$Theme4[i]))`

---


```{r, echo = FALSE}
i <- i + 1L
```

**Name:** `r abstracts$FirstName[i]` `r abstracts$LastName[i]`

**Supervisor:** `r abstracts$SFirstName[i]` `r abstracts$SLastName[i]`

**Title:** `r abstracts$Title[i]`

**Abstract:** `r abstracts$Abstract[i]`

**Tags:** `r ifelse(abstracts$Theme1[i] == "NA",TagFalse, abstracts$Theme1[i])``r ifelse(abstracts$Theme2[i] == "NA"," ", paste(", ", abstracts$Theme2[i]))``r ifelse(abstracts$Theme3[i] == "NA"," ", paste(", ", abstracts$Theme3[i]))``r ifelse(abstracts$Theme4[i] == "NA"," ", paste(", ", abstracts$Theme4[i]))`

---


```{r, echo = FALSE}
i <- i + 1L
```

**Name:** `r abstracts$FirstName[i]` `r abstracts$LastName[i]`

**Supervisor:** `r abstracts$SFirstName[i]` `r abstracts$SLastName[i]`

**Title:** `r abstracts$Title[i]`

**Abstract:** `r abstracts$Abstract[i]`

**Tags:** `r ifelse(abstracts$Theme1[i] == "NA",TagFalse, abstracts$Theme1[i])``r ifelse(abstracts$Theme2[i] == "NA"," ", paste(", ", abstracts$Theme2[i]))``r ifelse(abstracts$Theme3[i] == "NA"," ", paste(", ", abstracts$Theme3[i]))``r ifelse(abstracts$Theme4[i] == "NA"," ", paste(", ", abstracts$Theme4[i]))`

---


```{r, echo = FALSE}
i <- i + 1L
```

**Name:** `r abstracts$FirstName[i]` `r abstracts$LastName[i]`

**Supervisor:** `r abstracts$SFirstName[i]` `r abstracts$SLastName[i]`

**Title:** `r abstracts$Title[i]`

**Abstract:** `r abstracts$Abstract[i]`

**Tags:** `r ifelse(abstracts$Theme1[i] == "NA",TagFalse, abstracts$Theme1[i])``r ifelse(abstracts$Theme2[i] == "NA"," ", paste(", ", abstracts$Theme2[i]))``r ifelse(abstracts$Theme3[i] == "NA"," ", paste(", ", abstracts$Theme3[i]))``r ifelse(abstracts$Theme4[i] == "NA"," ", paste(", ", abstracts$Theme4[i]))`

---


```{r, echo = FALSE}
i <- i + 1L
```

**Name:** `r abstracts$FirstName[i]` `r abstracts$LastName[i]`

**Supervisor:** `r abstracts$SFirstName[i]` `r abstracts$SLastName[i]`

**Title:** `r abstracts$Title[i]`

**Abstract:** `r abstracts$Abstract[i]`

**Tags:** `r ifelse(abstracts$Theme1[i] == "NA",TagFalse, abstracts$Theme1[i])``r ifelse(abstracts$Theme2[i] == "NA"," ", paste(", ", abstracts$Theme2[i]))``r ifelse(abstracts$Theme3[i] == "NA"," ", paste(", ", abstracts$Theme3[i]))``r ifelse(abstracts$Theme4[i] == "NA"," ", paste(", ", abstracts$Theme4[i]))`

---






